EE454 Project 1 Report

### 2015-09-24 p1/report/latex/draft.tex
idk

@@

Design implementations were also taken closely into consideration. Our Matlab coding reflects procedural programming more commonly found in the C language. This was done in creating supporting files, functional programming, and nested for loop structures.  A few of the supporting files consisted of the convolve, the ReLU, and the maxpool function. Function calls in the neuralNet script called to these functions passing the necessary parameters along with it. These functions are much like functional programming in c++ where the purpose is to have a module or block of program code that handles a particular task.  These modules come in handy for being reusable.  By implementing this into our neural net we are able to greatly reduce the number of lines in our code while at the same time making it more robust. We have assurance in the function that when we call that section of code to handle a specific job it will stand by itself.  Digging deeper into these function modules there was also some design implementation at a lower level.  In the project description under the basic operations all of the computational building blocks defined using summations. For example in fully connected the output is determined by summations in all dimensions of the image including the rows columns and channels. We extracted this summation notation and created nested for loop structures to handle looping through all iterations of the dimensions and computing the summations in a totaling type of way. In fact the for loop structure was used throughout the project even in the neuralNet code.  It was decided that the for loop be used here for the vast amount of images that have to be run through the CNN to produce the probability vectors.

>>>>

Given a set of images where each image falls into a class, the neural net should be able to take the image as input and label the image.

@@

Design implementations were also taken closely into consideration. Our Matlab coding reflects procedural programming more commonly found in the C language. This was done in creating supporting files, functional programming, and nested for loop structures.  A few of the supporting files consisted of the convolve, the ReLU, and the maxpool function. Function calls in the neuralNet script called to these functions passing the necessary parameters along with it. These functions are much like functional programming in c++ where the purpose is to have a module or block of program code that handles a particular task.  These modules come in handy for being reusable.  By implementing this into our neural net we are able to greatly reduce the number of lines in our code while at the same time making it more robust. We have assurance in the function that when we call that section of code to handle a specific job it will stand by itself.  Digging deeper into these function modules there was also some design implementation at a lower level.  In the project description under the basic operations all of the computational building blocks defined using summations. For example in fully connected the output is determined by summations in all dimensions of the image including the rows columns and channels. We extracted this summation notation and created nested for loop structures to handle looping through all iterations of the dimensions and computing the summations in a totaling type of way. In fact the for loop structure was used throughout the project even in the Neural Net code.  It was decided that the for loop be used here for the vast amount of images that have to be run through the CNN to produce the probability vectors.
